### 2019-11-11 design.tex
aditya comments on S5, S6

\para{DC1. Construct the overview in-situ}
An overview helps users get a high-level picture
of the data.
However, maintaining the overview in a separate
location from the data can \newsaj{lead to loss of context};
instead, having it co-located with the data
can help users make rapid glances to
explore information between a
bird's-eye view
and a close-up detail~\cite{grudin2001partitioning}.

\para{DC2. Ensure reduced
visual discontinuity while providing details on demand}
Users often need to access subsets of data,
and study their properties in detail, \eg via steering.
Navigating back and forth \saj{between different subsets of data}
can lead to increased visual discontinuity.
The interface should allow users to compute such details for
various data subsets on demand~\cite{shneiderman2003eyes}.
The interface should maintain visual continuity
as users navigate to a different subset,
recomputing the details for the new subset.

\para{DC3. Balance the screen space afforded to the overview}
As the overview
has limited screen-space available,
we need to consider the trade-off between visual discontinuity (\emph{DC2}) and clarity.
\saj{Displaying a fine-grained overview improves visual clarity while increasing visual discontinuity---users need to scroll through the overview to access distant
subsets of data.
Displaying a coarse-grained overview decreases visual discontinuity at cost of reduced visual clarity---the overview may span too many data subsets and appear visually cluttered}.
The interface should further allow users to control the screen-space allocated
to the overview.

@@

\noah constructs the overview in-situ ({\bf DC1})
next to the spreadsheet
on an attribute of the spreadsheet dataset
called the {\em navigation attribute},
selected by the user.
Any attribute type that can be ordered
can be a navigation attribute, \eg
text, numbers.
The overview is constructed at multiple granularities.
Each granularity is divided into non-overlapping
groups of data called {\em bins}.
As shown in Figure~\ref{fig:concept}d,
an overview of the Airbnb data
on the navigation attribute ``city''
has granularity levels.
The highest (coarsest) granularity level
consists of four bins.
Figure~\ref{fig:concept}a
depicts the first four bins,
the first of which is {\em Ashville-Boston}.
Each bin contains summary information
regarding the data subset/region
it spans, \eg starting row and
ending row number, and 
the total number of rows the region spans.
Each bin displays an overview
of the next (finer) granularity (if any)
with embedded bar charts.
For example, in Figure~\ref{fig:concept}d,
the topmost bin ({\em Ash-Bos}) spans three cities
({\em Ashville}, {\em Austin}, {\em Boston}), each of which is a bin
in the next (finer) granularity.
Correspondingly, Figure~\ref{fig:concept}(a)
shows three horizontal bar charts for the
first {\em Ash-Bos} bin,
one for each bin in the next granularity.
Since the third bin from the top
(\emph{LA}) spans only one city,
no bar chart is embedded.
Users can perform different
operations on the bins, \eg clicking to pan and
semantic zooming in/out~\cite{perlin1993pad}.
\noah supports other interactions,
\eg customization and aggregation.
We discuss these interactions
in the context of our design considerations in Section~\ref{sec:overview_operations}.

\stitle{Why a Multi-granularity Binned Overview?}
\saj{A standard overview approach
is to show a spatially partitioned
collection of thumbnails \saj{on the left of the detailed view},
similar to Microsoft PowerPoint or
Adobe Reader.
However, displaying too many thumbnails
results in increased scrolling
to access distant thumbnails,
increasing visual discontinuity.
On the other hand,
displaying too few thumbnails
reduces visual discontinuity,
but at the cost of visual
clarity---the thumbnails appear cluttered
and fail to represent the
underlying data clearly~\cite{cockburn2009review}.
To strike a balance between these two objectives
({\bf DC3}) we designed a multi-granularity overview
that abstracts the data at varying levels of detail.
Multi-granularity interfaces
provide an alternative to \newsaj{the spatially partitioned single-granularity representation of the data space, \eg in Powerpoint, by allowing users to control the scale at which the overview should be displayed~\cite{cockburn2009review}.}
Users can resize the overview to control the amount of spreadsheet data that remains visible.
\toappendix{Microsoft PowerPoint also uses a
similar technique to balance the screen
space between overview and detail.}
Users can also hide the overview if required.}

\newsaj{The data structure underlying the overview
is an equi-depth histogram constructed
on the values
in the navigation attribute column.
Equi-depth histograms are commonly
used for summarizing the statistical properties
of data, with applications such as
database query optimizers~\cite{chaudhuri1998random}.
The binned representation of the overview
using equi-depth histograms
enables faster navigation
by reducing visual discontinuity. 
The bins act as landmarks
in the overview, enabling 
users to skip irrelevant bins
and quickly navigate to the desired subset of data. We now discuss how the overview is constructed.}

\stitle{Overview Construction.}
\newsaj{The equi-depth histogram 
can be constructed on 
any data types
that can be ordered, \eg text, numbers, dates. For example, 
in the usage scenario explained in Section~\ref{sec:usage},
the journalist grouped the data into cities
for ease of navigation 
when exploring the larger cities
in the Airbnb dataset.}
Each bin in the equi-depth histogram
contains the same number of items,
where each item is a value.
For example,
when constructing the overview
on city,
each value in the city column
is assigned to a bin.
The bins are constructed top-down
(see Figure~\ref{fig:concept}d). \noah divides
each of the bins at level $k$ into new bins
to construct the next lower level $k+1$, again,
by applying the same concept of equi-depth histograms.
If each value of the navigation attribute
column was unique, \eg if it was a numerical ID,
then construction of the histogram would be easy:
each bin of the equi-depth histogram
would contain almost the same number of items,
where each item corresponds to one unique value of
the attribute.
Unfortunately, in practice, for many attributes,
the same value is often repeated.
For example,
there are multiple listings
per city.
Therefore,
an equi-depth histogram
on the
attribute city
will result in consecutive bins
sharing items of
the same unique city value,
resulting in undesirable overlap.
Instead,
we construct a best effort
equi-depth
histogram that is as close to an equi-depth
histogram as possible, while ensuring
that the ranges represented by each bin have no overlap.
\agp{Aditya: would be valuable to describe the algorithm to increase
technical depth.}
\saj{Saj: can we add a pseudocode in appendix and refer to that?}

@@

\stitle{Navigational Operation: Semantic Zooming.}  
Users can zoom into a specific bin
to view more fine-grained information or zoom out
to view more coarse-grained information,
via semantic zooming~\cite{perlin1993pad}.
For example, in Figure~\ref{fig:concept}a,
from the bin \emph{Ashville-Boston}
when the user zooms in to the next level,
\noah displays the bins \emph{Ashville}, \emph{Austin},
and \emph{Boston} (Figure~\ref{fig:concept}b).
If the user zooms out of the current granularity, again \noah displays the bins \emph{Ashville-Boston}, \emph{Chicago-Denver}, and others.
Users can only zoom into any bin that
contains multiple unique values.
For example, in Figure~\ref{fig:concept}d, at level 2,
each bin corresponds to one city.
Therefore, users can only click on those bins
to bring that data into view, and cannot zoom in further.
One issue with zooming interactions
is discoverability \saj{of the zoom operation}~\cite{cockburn2009review}.
We circumvent this (see Figure~\ref{fig:concept}c)
by providing the root of the bin under selection
for zoom out, and arrows for
clicking to zoom in (``\textcolor{blue}{$\rangle$}'') and out (``\textcolor{blue}{$\langle$}'').

@@

\subsubsection{Coordination Between Overview and Spreadsheet}
\noah supports coordination
between the overview and the
corresponding spreadsheet data (\textbf{DC4}),
\ie interactions on the overview
may be reflected on the spreadsheet and vice-versa.
\newsaj{One example of this coordinations is,} indicating the navigation attribute on the spreadsheet
using color (see the lime green column in Figure~\ref{fig:ux}c)
as user constructs the overview. However, not all overview interactions are coupled
with the spreadsheet and vice versa.
The coupling depends on the user's current
focus---\emph{\saj{to ensure consistency between the overview and the spreadsheet,} any interaction on
either interface
that changes the current focus must be reflected
on the other interface}.
We now provide examples of both
coupled and decoupled interactions.

@@

Creating an aggregate column on the overview mimics how users create pivot tables. Users
are not required to explicitly type formulae;
rather they simply select the formula from a drop-down menu,
and provide the necessary formula parameters to a form.
\newsaj{The aggregate column can employ any} statistical
and mathematical formulae that
operate over a range of data.
\newsaj{Therefore, creating an aggregate column
is equivalent to selecting subsets of data
on the sheet, \ie steering, and then executing a formula on this subset},
helping users avoid cumbersome steering operations.
We have classified the formulae supported
into five categories: a) summary (\eg min, max, average),
b) frequency (\eg mode, large, small), c) conditional (\eg countif, sumif), d) spread (\eg var,stdev), and e) others (\eg sum, count).

>>>>

\para{DC1. Construct the overview in-situ}
An overview helps users get a high-level picture
of the data.
However, maintaining the overview in a separate
location from the data can \new{lead to loss of context};
instead, having it co-located with the data
can help users make rapid glances to
explore information between a
bird's-eye view
and a close-up detail~\cite{grudin2001partitioning}.

\para{DC2. Ensure reduced
visual discontinuity while providing details on demand}
Users often need to access subsets of data,
and study their properties in detail, \eg via steering.
Navigating back and forth \new{between different subsets of data}
can lead to increased visual discontinuity.
The interface should allow users to compute such details for
various data subsets on demand~\cite{shneiderman2003eyes}.
The interface should maintain visual continuity
as users navigate to a different subset,
recomputing the details for the new subset.

\para{DC3. Balance the screen space afforded to the overview}
As the overview
has limited screen-space available,
we need to consider the trade-off between visual discontinuity (\emph{DC2}) and clarity.
\new{Displaying a fine-grained overview improves visual clarity 
while increasing visual discontinuity---users need to scroll through the overview to access distant
subsets of data.
Displaying a coarse-grained overview decreases visual discontinuity 
at cost of reduced visual clarity---the overview may 
span too many data subsets and appear visually cluttered.}
The interface should further allow users to control the screen-space allocated
to the overview.

@@

\noah constructs the overview in-situ ({\bf DC1})
next to the spreadsheet
on an attribute of the spreadsheet dataset
called the {\em navigation attribute},
selected by the user.
Any attribute type that can be ordered
can be a navigation attribute, \eg
text, numbers.
The overview is constructed at multiple granularities.
Each granularity is divided into non-overlapping
groups of data called {\em bins}.
As shown in Figure~\ref{fig:concept}d,
an overview of the Airbnb data
on the navigation attribute ``city''
has granularity levels.
The highest (coarsest) granularity level
consists of four bins.
Figure~\ref{fig:concept}a
depicts the first four bins,
the first of which is {\em Ashville-Boston}.
Each bin contains summary information
regarding the data subset/region
it spans, \eg starting row and
ending row number, and 
the total number of rows the region spans.
Each bin displays an overview
of the next (finer) granularity (if any)
with embedded bar charts.
For example, in Figure~\ref{fig:concept}d,
the topmost bin ({\em Ash-Bos}) spans three cities
({\em Ashville}, {\em Austin}, {\em Boston}), each of which is a bin
in the next (finer) granularity.
Correspondingly, Figure~\ref{fig:concept}(a)
shows three horizontal bar charts for the
first {\em Ash-Bos} bin,
one for each bin in the next granularity.
Since the third bin from the top
(\emph{LA}) spans only one city,
no bar chart is embedded.
Users can perform different
operations on the bins, \eg clicking to pan and
semantic zooming in/out~\cite{perlin1993pad}.
\noah supports other interactions \new{atop this multi-granularity overview,}
\eg customization and aggregation.
We discuss these interactions
in the context of our design considerations in Section~\ref{sec:overview_operations}.

\stitle{Why a Multi-granularity Binned Overview?}
\new{A conventional design for overviews within
popular interfaces is as a spatially partitioned
collection of thumbnails 
on the left of the standard detailed view,
similar to Microsoft Power Point or
Adobe Reader.
However, displaying too many thumbnails
results in increased scrolling
to access distant thumbnails,
increasing visual discontinuity.
On the other hand,
displaying too few thumbnails
reduces visual discontinuity,
but at the cost of visual
clarity---the thumbnails appear cluttered
and fail to represent the
underlying data clearly~\cite{cockburn2009review}.
To strike a balance between these two objectives
({\bf DC3}) we designed a multi-granularity overview
that abstracts the data at varying levels of detail.
Multi-granularity representations have been shown to
scale better to 
larger datasets----presenting information 
at multiple granularities
makes visual representations
more perceptually scalable
and less cluttered~\cite{elmqvist2009hierarchical}.
Thus, the multi-granularity overview of \noah
provides an alternative to the aforementioned conventional 
spatially partitioned 
single-granularity representation of the data space, \eg in Power Point, 
by allowing users to control the scale at 
which the overview should be displayed~\cite{cockburn2009review}.
Users can resize the overview to control the amount of spreadsheet data that remains visible.
\toappendix{Microsoft PowerPoint also uses a
similar technique to balance the screen
space between overview and detail.}
Users can also hide the overview if required.}

\new{The data structure underlying the overview
is an equi-depth histogram constructed
on the values
in the navigation attribute column.\agp{Briefly describe what equi-depth histograms are; or don't mention it here, just say histogram -- we can defer details later}
Equi-depth histograms are commonly
used for summarizing the statistical properties
of data, with applications such as
database query optimizers~\cite{chaudhuri1998random}. \agp{only one application?}
The binned representation 
of the overview
using equi-depth histograms 
aggregates data 
and visualizes density 
by counting 
the number of data points 
falling within each bin. \agp{This previous sentence feels repetitive.}
Binned aggregation 
highlights both high level (\eg densities) and low level (e.g., outliers)
details of large datasets, 
while enabling
multi-granularity representation of data
via the choice of bin size~\cite{liu2013immens}. \agp{Clarify what is known from prior work and what
you are proposing. Here, it is intermixed.}
Moreover, binning reduces 
visual discontinuity during navigation
as users are able to 
view an overview 
that fits in the computer screen.
As a result, users can 
quickly navigate the data---the bins act as landmarks
in the overview, enabling 
users to skip irrelevant bins
and quickly navigate to the desired subset of data. We now discuss how the overview is constructed.}

\stitle{Overview Construction.}
\new{The equi-depth histogram 
can be constructed on 
any data types
that can be ordered, \eg text, numbers, dates. For example, 
in the usage scenario explained in Section~\ref{sec:usage},
the journalist grouped the data into cities
for ease of navigation 
when exploring the larger cities
in the Airbnb dataset.}
Each bin in the equi-depth histogram
contains the same number of items,
where each item is a value.
For example,
when constructing the overview
on city,
each value in the city column
is assigned to a bin.
The bins are constructed top-down
(see Figure~\ref{fig:concept}d). \noah divides
each of the bins at level $k$ into new bins
to construct the next lower level $k+1$, again,
by applying the same concept of equi-depth histograms.
If each value of the navigation attribute
column was unique, \eg if it was a numerical ID,
then construction of the histogram would be easy:
each bin of the equi-depth histogram
would contain almost the same number of items,
where each item corresponds to one unique value of
the attribute.
Unfortunately, in practice, for many attributes,
the same value is often repeated.
For example,
there are multiple listings
per city.
Therefore,
an equi-depth histogram
on the
attribute city
will result in consecutive bins
sharing items of
the same unique city value,
resulting in undesirable overlap.
Instead,
we construct a best effort
equi-depth
histogram that is as close to an equi-depth
histogram as possible, while ensuring
that the ranges represented by each bin have no overlap.
\agp{Aditya: would be valuable to describe the algorithm to increase
technical depth.}
\saj{Saj: can we add a pseudocode in appendix and refer to that?}
\agp{Yes please.}

@@

\stitle{Navigational Operation: Semantic Zooming.}  
Users can zoom into a specific bin
to view more fine-grained information or zoom out
to view more coarse-grained information,
via semantic zooming~\cite{perlin1993pad}.
For example, in Figure~\ref{fig:concept}a,
from the bin \emph{Ashville-Boston}
when the user zooms in to the next level,
\noah displays the bins \emph{Ashville}, \emph{Austin},
and \emph{Boston} (Figure~\ref{fig:concept}b).
If the user zooms out of the current granularity, again \noah displays the bins \emph{Ashville-Boston}, \emph{Chicago-Denver}, and others.
Users can only zoom into any bin that
contains multiple unique values.
For example, in Figure~\ref{fig:concept}d, at level 2,
each bin corresponds to one city.
Therefore, users can only click on those bins
to bring that data into view, and cannot zoom in further.
One issue with zooming interactions
is discoverability \new{of the zoom operation}~\cite{cockburn2009review}.
We circumvent this (see Figure~\ref{fig:concept}c)
by providing the root of the bin under selection
for zoom out, and arrows for
clicking to zoom in (``\textcolor{blue}{$\rangle$}'') and out (``\textcolor{blue}{$\langle$}'').

@@

\subsubsection{Coordination Between Overview and Spreadsheet}
\noah supports coordination
between the overview and the
corresponding spreadsheet data (\textbf{DC4}),
\ie interactions on the overview
may be reflected on the spreadsheet and vice-versa.
\new{One example of this coordinations is} indicating the navigation attribute on the spreadsheet
using color (see the lime green column in Figure~\ref{fig:ux}c)
as user constructs the overview. However, not all overview interactions are coupled
with the spreadsheet and vice versa.
The coupling depends on the user's current
focus---\emph{\new{to ensure consistency between the overview and the spreadsheet,} any interaction on
either interface
that changes the current focus must be reflected
on the other interface}.
We now provide examples of both
coupled and decoupled interactions.

@@

Creating an aggregate column on the overview mimics how users create pivot tables. Users
are not required to explicitly type formulae;
rather they simply select the formula from a drop-down menu,
and provide the necessary formula parameters to a form.
\new{The aggregate column can employ any statistical
or mathematical formulae that
operate over a range of data.
Therefore, creating an aggregate column
is equivalent to selecting subsets of data
on the sheet, \ie steering, and then executing a formula on this subset},
helping users avoid cumbersome steering operations.
We have classified the formulae supported
into five categories: a) summary (\eg min, max, average),
b) frequency (\eg mode, large, small), c) conditional (\eg countif, sumif), d) spread (\eg var,stdev), and e) others (\eg sum, count).

### 2019-11-11 letter.tex
aditya comments on S5, S6

\new{We thank the reviewers and meta-reviewer for their detailed,

@@

the changes are highlighted in blue.

@@

Furthermore, in Section~\ref{sec:intro},  

@@

interactions like scrolling and steering have been augmented, and 
we now clearly articulate the challenges of 

@@

clarify the scope of tasks supported by spreadsheets and enhanced
by a spreadsheet with a \noah plug-in; our new Table~\ref{tab:scope}

@@

we opted for histograms as an overview representation. 

@@

rather, they have been grouped together and made less
ambiguous. In this version,

@@

}

@@

\item \textit{Merits over other tools} (\textbf{C1}): 
\new{Throughout the paper (and especially in 
Sections~\ref{sec:intro}, \ref{sec:related},
and \ref{sec:study}), we have emphasized
that the main contribution of \noah
is its \emph{design as a general-purpose navigation plug-in} 
to any existing spreadsheet system. 
As spreadsheets have a massive user-base, 
enhancing exploration and formula computation 
on large datasets while maintaining 
the spreadsheet look-and-feel as much as possible, 
has the potential to impact hundreds of millions 
of spreadsheet users. 
Most of these users employ spreadsheets 
as their primary data management and analysis 
tool while shunning enterprise solutions 
with more advanced features. 
Therefore, our goal is to develop a 
solution to improve navigation within spreadsheets.
Indeed, we could have tried to enhance navigation
in other tools, such as Keshif, or Tableau, like
the reviewers suggest---but we would be forcing
spreadsheet users to adopt an entirely new tool, something
that they are clearly loath to do.}

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): 
\new{We now explain our choice
of the binning mechanism in 
the context of the third design consideration (\emph{DC3}), 
as detailed in Section~\ref{sec:design}.
We further expand on this in the blurb titled 
``Why a Multi-granularity Binned Overview'' 
in Section~\ref{sec:ui}.
In brief, we opted for binning to 
provide a clear and concise 
representation of the overall data 
distribution while minimizing user's back 
and forth movement across multiple screens 
during navigation. 
At some level, we do need to limit the number
of values displayed so that the overview
fits on the screen: binning is a natural solution
for that issue. 
\agp{Possibly argue using the immens paper?}
\newsaj{We cite related work on 
multi-scale aggregation~\cite{elmqvist2009hierarchical} 
to motivate the choice of 
a multi-granularity overview
and show that binned aggregation via histogram~\cite{liu2013immens}
is a suitable representation of such an overview.}
However, we acknowledge limitations 
for this choice for binning categorical data 
and discuss possible solutions 
in Section~\ref{sec:discuss} 
in the context of our user study findings. 
}

\item \textit{Justification of Excel as a Baseline} (\textbf{C3}):
\new{Since our goal is to improve spreadsheet
user experience---and there are very good reasons for doing so,
as outlined in item 1) above---the natural comparison point
is Excel. 
That said, beyond popularity, 
we have provided a thorough justification
for what spreadsheet systems like Excel offer
relative to tabular data analysis tools (TDA),
making it a more appropriate point of comparison.
Our justification for using Excel over 
tabular data analysis (TDA) tools involves 
a) highlighting the appeal of spreadsheets 
among users who shun more advanced enterprise 
tools (Section~\ref{sec:intro}), 
b) identifying the scope of tasks 
supported by spreadsheets and 
TDA tools (Section~\ref{sec:usage} and~\ref{sec:related}), 
c) explaining that the goal of spreadsheets 
is to present the raw data as is, 
amenable to editing, formula computation, and comparison of derived data, all done in-situ,
unlike TDA tools that hide the data 
while providing summarized statistics 
(Section~\ref{sec:related}), and 
d) highlighting the importance of 
addressing the shortcomings of a tool, 
the user base of which far exceeds 
that of TDA tools (Section~\ref{sec:study}). 
}

\item \textit{Enhancing the user study design} 
(\textbf{C4, C5}):
\agp{Revise to clarify where these changes are made
and HOW these changes solve the issue. Just saying
we merged doesn't necessarily address the issue.}
We have added additional 
explanations regarding the goal 
of the study while better articulating 
the research questions, provided a better justification for the choice of the tasks for the study (see Section~\ref{sec:study_design}) and added a detailed discussion on the limitations of the study. \newsaj{Specifically, we merged our previous \emph{RQ1} (evaluating the quiz task performance) with \emph{RQ4} (summarizing user feedback on performance via survey) into a unified research question (new \emph{RQ1}) on participants' navigation performance. Moreover, we merged a previous \emph{RQ2} and \emph{RQ3} that explored how specific features of \noah affected participants' navigation experience into one broad question (new \emph{RQ2}) which explores their overall experience with \noah and its components}. Moreover, we have justified the choice of the quiz tasks by a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}), and b) explaining how these tasks can reveal how people may use \noah for spreadsheet navigation. Finally, we have identified three limitations of the study, resulting from the sample size and the study design, which we justify based on the scope of the study.

>>>>

We thank the reviewers and meta-reviewer for their detailed,

@@

the changes are highlighted in \new{blue}.

@@

We further augment   

@@

interactions like scrolling and steering in Section~\ref{sec:intro}, 
and now clearly articulate the challenges of 

@@

clarify the scope of tasks supported by spreadsheets, as well
as those that are enhanced
when using a spreadsheet with a \noah plug-in; our new Table~\ref{tab:scope}

@@

we opted for histograms as an overview representation, \new{by contextualizing our
approach using prior work on multi-scale aggregation~\cite{elmqvist2009hierarchical}.} 

@@

rather, they have been grouped together and made more precise. 
In this version,

@@

@@

\item \textit{Merits over other tools} (\textbf{C1}): 
Throughout the paper (and especially in 
Sections~\ref{sec:intro}, \ref{sec:related},
and \ref{sec:study}), we have emphasized
that the main contribution of \noah
is its \emph{design as a general-purpose navigation plug-in} 
to any existing spreadsheet system. 
As spreadsheets have a massive user-base, 
enhancing exploration and formula computation 
on large datasets while maintaining 
the spreadsheet look-and-feel as much as possible, 
has the potential to impact hundreds of millions 
of spreadsheet users. 
Most of these users employ spreadsheets 
as their primary data management and analysis 
tool while shunning enterprise solutions 
with more advanced features. 
Therefore, our goal is to develop a 
solution to improve navigation within spreadsheets.
Indeed, we could have tried to enhance navigation
in other tools, such as Keshif, or Tableau, like
the reviewers suggest---but we would be forcing
spreadsheet users to adopt an entirely new tool, something
that they are clearly loath to do.

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): 
We now explain our choice
of the binning mechanism in 
the context of the third design consideration (\emph{DC3}), 
as detailed in Section~\ref{sec:design}.
We further expand on this in the blurb titled 
``Why a Multi-granularity Binned Overview'' 
in Section~\ref{sec:ui}.
In brief, we opted for binning to 
provide a clear and concise 
representation of the overall data 
distribution while minimizing user's back 
and forth movement across multiple screens 
during navigation. 
At some level, we do need to limit the number
of values displayed so that the overview
fits on the screen: binning is a natural solution
for that issue. 
We cite related work on 
multi-scale aggregation~\cite{elmqvist2009hierarchical} 
to motivate the choice of 
a multi-granularity overview
and show that binned aggregation via histograms~\cite{liu2013immens}
is a suitable representation of such an overview.
However, we acknowledge limitations 
for this choice for binning categorical data 
and discuss possible solutions 
in Section~\ref{sec:discuss} 
in the context of our user study findings.

\item \textit{Justification of Excel as a Baseline} (\textbf{C3}):
Since our goal is to improve spreadsheet
user experience---and there are very good reasons for doing so,
as outlined in item 1) above---the natural comparison point
is Excel. 
That said, beyond popularity, 
we have provided a thorough justification
for what spreadsheet systems like Excel offer
relative to tabular data analysis tools (TDA),
making it a more appropriate point of comparison.
Our justification for using Excel over 
tabular data analysis (TDA) tools involves 
a) highlighting the appeal of spreadsheets 
among users who shun more advanced enterprise 
tools (Section~\ref{sec:intro}), 
b) identifying the scope of tasks 
supported by spreadsheets and 
TDA tools (Section~\ref{sec:usage} and~\ref{sec:related}), 
c) explaining that the goal of spreadsheets 
is to present the raw data as is, 
amenable to editing, formula computation, 
and comparison of derived data, all done in-situ,
unlike TDA tools that hide the data 
while providing summarized statistics 
(Section~\ref{sec:related}), and 
d) highlighting the importance of 
addressing the shortcomings of a tool, 
the user base of which far exceeds 
that of TDA tools (Section~\ref{sec:study}).

\item \textit{Enhancing the user study design} 
(\textbf{C4, C5}):
We have added additional 
explanations regarding the goals 
of the study while better articulating 
the research questions, 
provided a better justification 
for the choice of the tasks for the study (see Section~\ref{sec:study_design}) 
and added a detailed discussion on the limitations of the study. 
Specifically, we merged our previous \emph{RQ1} (evaluating the quiz task performance) 
with \emph{RQ4} (summarizing user feedback on performance via a survey) 
into a unified research question (new \emph{RQ1}) 
on the participants' navigation performance. 
Moreover, we merged previous \emph{RQ2} and \emph{RQ3} 
that explored how specific features of \noah 
affected participants' navigation experience 
into one broad question (new \emph{RQ2}) 
that explores their overall experience with \noah and its components. 
Moreover, we have justified the choice of the quiz tasks by 
a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}), 
and b) explaining how these tasks can reveal how people may use \noah 
for spreadsheet navigation. 
Finally, we have identified three limitations of the study, 
resulting from the sample size and the study design, which we justify based on the scope of the study.

### 2019-11-11 usecases.tex
aditya comments on S5, S6

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including \newsaj{analytical reasoning during exploration~\cite{shrinivasan2008supporting}, multi-dimensional data analysis~\cite{valiati2006taxonomy}, graph comprehension~\cite{friel2001making}, cartography~\cite{roth2012empirically}, among others.}\agp{argue for
 utility with citations.} \agp{This doesn't cut it because i wanted to argue that it HAS been used, not that it can be used. So can we find citations post 2013?.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}

>>>>

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including
developing models for visualization system design~\cite{meyer2015nested}, 
designing task taxonomies for cartograms~\cite{mcnabb2017survey}, 
and defining the scope of tasks in a number of domains, 
\eg interactive task authoring~\cite{fulda2015timelinecurator},
 document mining~\cite{brehmer2014overview}, 
 multivariate network analysis~\cite{pretorius2014tasks}, 
 mass cytometry~\cite{hollt2016cytosplore}, among others.
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}
